%-------------------------
% Resume in Latex
% Author : Devansh Sabharwal
% Based off of: https://github.com/Devansh-Sabharwal/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}\renewcommand{\baselinestretch}{0.95}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks=true ,colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=green]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{setspace}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{2.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Devansh Sabharwal} \\ \vspace{1pt}
    \small +91 6280297457 $|$ \faEnvelope \hspace{0.1cm} \href{mailto:x@x.com}{\underline{
  sabharwaldevansh04@gmail.com}} $|$ 
     \href{https://devanshsabharwal.vercel.app}{\underline{Portfolio}} $|$
     \href{https://linkedin.com/in/devanshsabharwal}{\underline{Linkedin}} $|$
    \href{https://github.com/Devansh-Sabharwal}{\underline{Github }} $|$
    \href{https://x.com/Devansh2k4}{\underline{Twitter}}
    
\end{center}


%-----------EDUCATION-----------
\section{\Large Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Punjabi University Patiala}{\textbf{CGPA 9.18}}
      {Bachelor of Technology in Computer Science}{Aug 2022 – May 2026}

\resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{\Large Projects}
    \resumeSubHeadingListStart

    \resumeProjectHeading
           {\large \textbf{Visura} $|$ \emph{2D AI Animation Generator} 
           \href{https://visura.space/}{Live Demo} $|$    \href{https://github.com/Devansh-Sabharwal/visura}{Github}}{Jun 2025 – Jul 2025 } 
\begin{itemize}[leftmargin=0.3in,label={$\bullet$}]
    
    \item Engineered Visura, an AI-driven system that transforms natural language prompts into high-quality 2D animations, reducing animation creation time by over 90\%.
    \item Deployed a FastAPI backend with Celery and Redis to enable asynchronous video rendering and handle 100+ daily requests with $<$ 2s script generation.
    \item Designed an LLM-style interface in Next.js for prompt input and seamless chat-based animation generation.
    \item Integrated Cloudinary for media storage and implemented background rendering tasks, reducing the user wait time for final animations by 60\%.
    \item Using Docker Compose to run a multiservice architecture (FastAPI, Redis, Celery), ensuring 99.9\% uptime and seamless scaling.
\end{itemize}

    
    \resumeProjectHeading
           {\large \textbf{CoScribe} $|$ \emph{Real-Time Collaborative Whiteboard}
           \href{https://coscribe.onrender.com/}{Live Demo} $|$
           \href{https://github.com/Devansh-Sabharwal/CoScribe}{Github}}{Feb 2025 – Mar 2025} 
           \begin{itemize}[label={$\bullet$}]

                \item Built a Excalidraw-style collaborative whiteboard platform using Next.js, WebSockets, and Tailwind CSS.
                \item Enabled real-time multi-user collaboration with a custom WebSocket-based broadcasting system.
                \item developed a scalable canvas supporting large teams, adopted by 120+ active users for real-time collaboration.
                \item Added room-based and authentication permissions for secure team and classroom use.
                \item Devised and implemented core collaboration tools, drawing, erasing, shape creation, entirely from scratch.
                \end{itemize}
                

    

    \resumeProjectHeading
           {\large \textbf{BrainDock} $|$ \emph{MERN Stack}
           \href{https://braindock.vercel.app}{Live Demo}  $|$   \href{https://github.com/Devansh-Sabharwal/BrainDock}{Github}}{Dec 2024} 
            \begin{itemize}[label={$\bullet$}]
               
                \item {Developed a centralized platform used by 50+ users to store and categorize YouTube videos, tweets, Notion documents, and websites in one location.}
                \item {Enabled curated link sharing to enhance collaboration and knowledge exchange.}
                \item {Built a responsive user interface using React, TypeScript, and Tailwind CSS, achieving a 90\% satisfaction rate based on post-launch surveys and usability testing.}
                \item {
                Embedded YouTube videos and X posts directly into the platform, creating a smoother, more interactive user experience.
                }
            \end{itemize}

\resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{\Large Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
    \textbf{Languages}{: C/C++, Python, SQL, JavaScript, HTML/CSS} \\
    \textbf{Frontend}{: React, Zustand, Next.js, TypeScript, Tailwind CSS} \\
    \textbf{Backend}{: Node.js, Express, MongoDB, PostgreSQL, FastAPI, Prisma} \\
    \textbf{Developer Tools}{: Git, Docker, VS Code, Postman, Vercel, Cloudinary} \\
    \textbf{Others}{: Data Structures and Algorithms}
}}
 \end{itemize}

\section{\Large Achievements}
\begin{itemize}[leftmargin=0.15in, label={$\bullet$},itemsep=0pt]
    \item {\textbf{Global rank 816 }in LeetCode Weekly Contest 409 (36,000 participants)}\\
    \item {\textbf{Achieved a Knight rating (1950+)} on LeetCode, placing me in the\textbf{ top 3.5\%} of users globally (Global Standing: 24,193/644,080). 
    \item {\textbf{Solved 1500+ problems} on competitive coding platforms (Codeforces, LeetCode, CodeChef )\textbf{surpassing 99.7 \% of users on LeetCode.} }
    \item {Secured consistent top 5\% rankings in programming contests by optimizing algorithms and writing efficient solutions under strict time limits.}
     \item {\textbf{Codeforces handle:} \href{https://codeforces.com/profile/sabharwaldevansh04}{sabharwaldevansh04}}
      {\textbf{  LeetCode profile:} \href{https://leetcode.com/u/CodeDEVotion/}{CodeDEVotion}}}

 \end{itemize}
%-------------------------------------------
\end{document}
